Tables with \textbf{xtable} and \textbf{knitr}

### 2016-10-10 src/ArticleReadyTableGenerate.Rnw
Modify printed table

    }
  }
  colnames(p_value_table)<- col_names
  xtab.out <- xtable(p_value_table)
  addtorow <- list()
  addtorow$pos <- list(0)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
    include.rownames=FALSE,
    type="latex")
# create a table of 7 comparisons
#

>>>>

    }
  }
  colnames(p_value_table)<- col_names
  p_value_table_print <- mapply(p_value_table, function(x){if (x<1E-4) return ("<0.0001") else{
    return(as.character(x,digits=4))
  }})
  xtab.out <- xtable(p_value_table_print)
  addtorow <- list()
  addtorow$pos <- list(0)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
    include.rownames=FALSE,
    type="latex")
# create a table of 7 comparisons
#
